---
title: "Untitled"
author: "Sophie Castel"
date: "4/6/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read .txt File

```{r}
data <- read_profilm(file = "/home/sophie/profilMALDI/data/test.txt")
data
```

## Change resolution 

```{r}
data_resized <- change_res(data, xres = 120, yres = 100)
```

### Example using volcano data

```{r}

data(volcano)
z <- volcano

data <- list()
data$surface <- volcano


z_resized <- change_res(data, xres = 20, yres = 20)

data_resized <- list()
data_resized$surface <- z_resized

p <- plot_profilm(data = data, palette = 'matlab_like', threeD = FALSE, tolerance = 10, contour_col = "white")

p_resized <- plot_profilm(data = data_resized, palette = 'matlab_like', threeD = FALSE, tolerance = 2, contour_col = "white")

grid.arrange(p, p_resized, nrow = 1)


```


### Create Example Standard (lower Right)
```{r}

squared <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 80:100){
  squared[i, ] <- sample(thick, size = 100)
}
for(j in 80:100){
  squared[, j] <- sample(thick, size = 100)
}

## Need to use pixel_size to scale properly. Rotation affects number of pixels and cant figure out algorithm for this. Try padding the matrix first and then rotating to see if it changes the scale of the important stuff
```


```{r}
# Original
test_mat <- matrix(1:2000, nrow = 100, ncol = 200)

# Start by padding matrix
scale_mat <- scale(x = test_mat, scale.row = 200, scale.col = 200)

# Then rotate
rot_mat <- rotate.matrix(x = scale_mat, angle = -4, method = "bilinear")

# Put in list to plot
rot_list <- list()
scale_list <- list()

rot_list$surface <- rot_mat
scale_list$surface <- scale_mat

p1 <- plot_profilm(data = scale_list, threeD = FALSE)
p2 <- plot_profilm(data = rot_list, threeD = FALSE)

grid.arrange(p1,p2, nrow = 1)

# Determine how much larger the rotated matrix became relative to the padded matrix

adj <- (dim(scale_mat)/dim(rot_mat))*100 # adjustment factors
names(adj) <- c("r.factor", "c.factor")
adj <- round(adj)

# Rescale rotated matrix to match padded original

t_list <- list()

t_list$surface <- scale(x = rot_mat, scale.row = adj["r.factor"] , scale.col = adj["c.factor"])

p3 <- plot_profilm(data = t_list, threeD = FALSE)

grid.arrange(p1,p2,p3,  nrow = 1)


```
 
# Create rotated text files
```{r}
squared <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 80:100){
  squared[i, ] <- sample(thick, size = 100)
}
for(j in 80:100){
  squared[, j] <- sample(thick, size = 100)
}


r1 <- rotate.matrix(x = squared, angle = 2, method = "bilinear")
r2 <- rotate.matrix(x = squared, angle = 3, method = "bilinear")
r3 <- rotate.matrix(x = squared, angle = 4, method = "bilinear")
r4 <- rotate.matrix(x = squared, angle = 5, method = "bilinear")
r5 <- rotate.matrix(x = squared, angle = 6, method = "bilinear")

r_list <- vector(mode = "list", length =5)

r_list[[1]]$surface <- r1[1:100, 1:100]
r_list[[2]]$surface <- r2[1:100, 1:100]
r_list[[3]]$surface <- r3[1:100, 1:100]
r_list[[4]]$surface <- r4[1:100, 1:100]
r_list[[5]]$surface <- r5[1:100, 1:100]

p1 <- plot_profilm(data = r_list[[1]]$surface, threeD = FALSE)
p2 <- plot_profilm(data = r_list[[2]]$surface, threeD = FALSE)
p3 <- plot_profilm(data = r_list[[3]]$surface, threeD = FALSE)
p4 <- plot_profilm(data = r_list[[4]]$surface, threeD = FALSE)
p5 <- plot_profilm(data = r_list[[5]]$surface, threeD = FALSE)

grid.arrange(p1,p2,p3,p4,p5, nrow = 1)

```

# Checking conforming data size
```{r}
dims <- list()
  
dims <- lapply(r_list, FUN = function(x) dim(x$surface))
  
logic_dims <- 
if(length(unique(dims)) != 1){
  stop("Data set ______ has non-conforming dimension. Adjusting size:")
}
```


# Increasing padding 

```{r}
# Just increase padding by a lot (nothing specific)
scale.row = 200
scale.col = 200
  
padded_list <- lapply(r_list, FUN = function(x){
  scale(x = x$surface, scale.row = scale.row, scale.col = scale.col)
})
  
# determine dimensions
  
dim_padded_list <- lapply(padded_list, FUN = function(x){
  dims <- dim(x)
  names(dims) <- c("rows","columns")
    return(dims)
})

p1 <- plot_profilm(data = padded_list[[1]], threeD = FALSE)
p2 <- plot_profilm(data = padded_list[[2]], threeD = FALSE)
p3 <- plot_profilm(data = padded_list[[3]], threeD = FALSE)
p4 <- plot_profilm(data = padded_list[[4]], threeD = FALSE)
p5 <- plot_profilm(data = padded_list[[5]], threeD = FALSE)

grid.arrange(p1,p2,p3,p4,p5, nrow = 1)

```

# Performing rotation

```{r}
# perform rotation correction, save in a list
  
standard_thickness = 5.5
tolerance = 0.5
standard_pos <- "lowerRight"

rotated_list <- lapply(padded_list, FUN = function(x){
  rotate(x = x, standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = standard_pos)
  })
  
# determine dimensions
  
dim_rotated_list <- lapply(rotated_list, FUN = function(x){
  dims <- dim(x)
  names(dims) <- c("rows","columns")
  return(dims)
})
  
# determine scale factors
adj_list <- mapply("/", dim_padded_list, dim_rotated_list, SIMPLIFY = FALSE)

adj_list <- lapply(adj_list, FUN = function(x){
  adjs <- round(x*100)
  names(adjs) <- c("r.factor", "c.factor")
  return(adjs)
})

p1 <- plot_profilm(data = rotated_list[[1]], threeD = FALSE)
p2 <- plot_profilm(data = rotated_list[[2]], threeD = FALSE)
p3 <- plot_profilm(data = rotated_list[[3]], threeD = FALSE)
p4 <- plot_profilm(data = rotated_list[[4]], threeD = FALSE)
p5 <- plot_profilm(data = rotated_list[[5]], threeD = FALSE)

grid.arrange(p1,p2,p3,p4,p5, nrow = 1)

```

# Maybe instead rotate until there are no zeroes in the row and column
# But this means angles have to be very precise
# So do a group

# Or until the first and last element in the row both contain nonzero elements

# Or until we have the last entire row of zeroes 
# As soon as the sum of the row is not zero




#Check trace algorithm
```{r}
# lower Right
squared1 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 70:100){
  squared1[i, ] <- sample(thick, size = 100)
}
for(j in 70:100){
  squared1[, j] <- sample(thick, size = 100)
}


# Upper right
squared2 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 1:20){
  squared2[i, ] <- sample(thick, size = 100)
}
for(j in 80:100){
  squared2[, j] <- sample(thick, size = 100)
}

# Upper Left
squared3 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(j in 1:20){
  squared3[, j] <- sample(thick, size = 100)
}

for(i in 1:20){
  squared3[i, ] <- sample(thick, size = 100)
}



# Lower Left
squared4 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 80:100){
  squared4[i, ] <- sample(thick, size = 100)
}
for(j in 1:20){
  squared4[, j] <- sample(thick, size = 100)
}


s1 <- plot_profilm(data = squared1, threeD = FALSE)
s2 <- plot_profilm(data = squared2, threeD = FALSE)
s3 <- plot_profilm(data = squared3, threeD = FALSE)
s4 <- plot_profilm(data = squared4, threeD = FALSE)

grid.arrange(s1,s2,s3,s4, nrow  =1)

t1 <- trace(squared1, standard_pos = "lowerRight")
t2 <- trace(squared2, standard_pos = "upperRight")
t3 <- trace(squared3, standard_pos = "upperLeft")
t4 <- trace(squared4, standard_pos = "lowerLeft")

```

# Check rotation algorithm
```{r}
standard_thickness = 5.5
tolerance = 0.5
standard_pos <- "lowerRight"
clockwise = FALSE

# Should be 2

pr1 <- rotate(x = padded_list[[1]], 
              standard_thickness = standard_thickness, 
              tolerance = tolerance, 
              standard_pos = standard_pos, 
              clockwise = clockwise)
pr1$rot_deg
pr1$rot_deg == 2


# 3

pr2 <- rotate(x = padded_list[[2]], 
              standard_thickness = standard_thickness, 
              tolerance = tolerance, 
              standard_pos = standard_pos, 
              clockwise = clockwise)
pr2$rot_deg
pr2$rot_deg == 3


# 4 

pr3 <- rotate(x = padded_list[[3]], 
              standard_thickness = standard_thickness, 
              tolerance = tolerance, 
              standard_pos = standard_pos, 
              clockwise = clockwise)
pr3$rot_deg
pr3$rot_deg == 4

# 5

pr4 <- rotate(x = padded_list[[4]], 
              standard_thickness = standard_thickness, 
              tolerance = tolerance, 
              standard_pos = standard_pos, 
              clockwise = clockwise)
pr4$rot_deg # WHY IS THIS ZERO
pr4$rot_deg == 5 
  
# 6

pr5 <- rotate(x = padded_list[[5]], 
              standard_thickness = standard_thickness, 
              tolerance = tolerance, 
              standard_pos = standard_pos, 
              clockwise = clockwise)
pr5$rot_deg
pr5$rot_deg == 6


prp1 <- plot_profilm(data = pr1$matrix, threeD = FALSE, palette = "matlab_like")
prp2 <- plot_profilm(data = pr2$matrix, threeD = FALSE, palette = "matlab_like")
prp3 <- plot_profilm(data = pr3$matrix, threeD = FALSE, palette = "matlab_like")
prp4 <- plot_profilm(data = pr4$matrix, threeD = FALSE, palette = "matlab_like")

# THIS IS HAPPENING BECAUSE THE TRIMMING ALGORITHM NEEDS TO MAKE SURE THAT IT TRIMS RELATIVE TO THE INNER CORNER. SUCH THAT ALL BOUNDARIES OF THE STANDARD THAT ARE TOUCHING THE EDGE OF THE MATRIX ARE NON ZERO.

# ALSO NEED TO PROGRAM THE ALGORITHM TO DETERMINE CLOCKWISE AND USE VERTICAL REFERENCE OR COUNTER CLOCKWISE AND USE HORIZONTAL REFERENCE. BASICALLY DETERMINE WHICH DIRECTION TO ROTATE

prp5 <- plot_profilm(data = pr5$matrix, threeD = FALSE, palette = "matlab_like")

grid.arrange(p1,p2,p3,p4,p5, nrow = 1)
grid.arrange(prp1, prp2, prp3, prp4, prp5, nrow = 1)
```

# Try trace algorithm

```{r}

r1c <- rotate.matrix(x = squared1, angle = -3) # lower right, need clockwise
r1cc <- rotate.matrix(x = squared1, angle = 3) # lower right, need counterclockwise

r2c <- rotate.matrix(x = squared2, angle = -3) # upper right, need clockwise
r2cc <- rotate.matrix(x = squared2, angle = 3) # upper right, need counterclockwise

r3c <- rotate.matrix(x = squared3, angle = -3) # upper left, need clockwise
r3cc <- rotate.matrix(x = squared3, angle = 3) # upper left, need counterclockwise

r4c <- rotate.matrix(x = squared4, angle = -3) # lower left, need clockwise
r4cc <- rotate.matrix(x = squared4, angle = 3) # lower left, need counterclockwise

r1 <- plot_profilm(data = r1c, threeD = FALSE)
r2 <- plot_profilm(data = r1cc, threeD = FALSE)
r3 <- plot_profilm(data = r2c, threeD = FALSE)
r4 <- plot_profilm(data = r2cc, threeD = FALSE)
r5 <- plot_profilm(data = r3c, threeD = FALSE)
r6 <- plot_profilm(data = r3cc, threeD = FALSE)
r7 <- plot_profilm(data = r4c, threeD = FALSE)
r8 <- plot_profilm(data = r4cc, threeD = FALSE)

grid.arrange(r1,r2,r3,r4,r5,r6,r7,r8, ncol = 2)


t1 <- trim(x = r1c, standard_pos = "lowerRight")
t2 <- trim(x = r1cc, standard_pos = "lowerRight")
t3 <- trim(x = r2c, standard_pos = "upperRight")
t4 <- trim(x = r2cc, standard_pos = "upperRight")
t5 <- trim(x = r3c, standard_pos = "upperLeft")
t6 <- trim(x = r3cc, standard_pos = "upperLeft")
t7 <- trim(x = r4c, standard_pos = "lowerLeft")
t8 <- trim(x = r4cc, standard_pos = "lowerLeft")

pt1 <- plot_profilm(data = t1, threeD = FALSE)
pt2 <- plot_profilm(data = t2, threeD = FALSE)
pt3 <- plot_profilm(data = t3, threeD = FALSE)
pt4 <- plot_profilm(data = t4, threeD = FALSE)
pt5 <- plot_profilm(data = t5, threeD = FALSE)
pt6 <- plot_profilm(data = t6, threeD = FALSE)
pt7 <- plot_profilm(data = t7, threeD = FALSE)
pt8 <- plot_profilm(data = t8, threeD = FALSE)

grid.arrange(pt1,pt2,pt3,pt4,pt5,pt6,pt7,pt8, ncol = 2)



```


# Checking with pseudo-trim

```{r}
tr1 <- r1c[10:90,10:90]
tr2 <- r1cc[10:90,10:90]
tr3 <- r2c[10:90,10:90]
tr4 <- r2cc[10:90,10:90]
tr5 <- r3c[10:90,10:90]
tr6 <- r3cc[10:90,10:90]
tr7 <- r4c[10:90,10:90]
tr8 <- r4cc[10:90,10:90]

ptr1 <- plot_profilm(data = tr1, threeD = FALSE)
ptr2 <- plot_profilm(data = tr2, threeD = FALSE)
ptr3 <- plot_profilm(data = tr3, threeD = FALSE)
ptr4 <- plot_profilm(data = tr4, threeD = FALSE)
ptr5 <- plot_profilm(data = tr5, threeD = FALSE)
ptr6 <- plot_profilm(data = tr6, threeD = FALSE)
ptr7 <- plot_profilm(data = tr7, threeD = FALSE)
ptr8 <- plot_profilm(data = tr8, threeD = FALSE)

grid.arrange(ptr1,ptr2,ptr3,ptr4,ptr5,ptr6,ptr7,ptr8, ncol = 2)

lrc <- trace(tr1, standard_pos = "lowerRight")
lrcc <- trace(tr2, standard_pos = "lowerRight")
urc <- trace(tr3, standard_pos = "upperRight")
urcc <- trace(tr4, standard_pos = "upperRight")
ulc <- trace(tr5, standard_pos = "upperLeft")
ulcc <- trace(tr6, standard_pos = "upperLeft")
llc <- trace(tr7, standard_pos = "lowerLeft")
llcc <- trace(tr8, standard_pos = "lowerLeft")

# Looks like its ok

```

# NOW JUST NEED TO IMPROVE TRIMMING ALGORITHM SO THAT THERE ARE SEAMLESS EDGES (NO BLUNT EDGES ZEROES) (This shouldn't pose an issue experimentally)
# From the top
# Create sample data with external standards in each corner
```{r}

# lower Right
squared1 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 80:100){
  squared1[i, ] <- sample(thick, size = 100)
}
for(j in 80:100){
  squared1[, j] <- sample(thick, size = 100)
}


# Upper right
squared2 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 1:20){
  squared2[i, ] <- sample(thick, size = 100)
}
for(j in 80:100){
  squared2[, j] <- sample(thick, size = 100)
}

# Upper Left
squared3 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(j in 1:20){
  squared3[, j] <- sample(thick, size = 100)
}

for(i in 1:20){
  squared3[i, ] <- sample(thick, size = 100)
}

# Lower Left
squared4 <- matrix(rep(0,1000), nrow = 100, ncol = 100)

thick <- seq(5.0, 5.9, length.out = 100)

for(i in 80:100){
  squared4[i, ] <- sample(thick, size = 100)
}
for(j in 1:20){
  squared4[, j] <- sample(thick, size = 100)
}


s1 <- plot_profilm(data = squared1, threeD = FALSE)
s2 <- plot_profilm(data = squared2, threeD = FALSE)
s3 <- plot_profilm(data = squared3, threeD = FALSE)
s4 <- plot_profilm(data = squared4, threeD = FALSE)

grid.arrange(s1,s2,s3,s4, nrow  =1)

```

# Perform all types of rotation to simulate actual data
```{r}
r1c <- rotate.matrix(x = squared1, angle = -3) # lower right, need clockwise
r1cc <- rotate.matrix(x = squared1, angle = 3) # lower right, need counterclockwise

r2c <- rotate.matrix(x = squared2, angle = -3) # upper right, need clockwise
r2cc <- rotate.matrix(x = squared2, angle = 3) # upper right, need counterclockwise

r3c <- rotate.matrix(x = squared3, angle = -3) # upper left, need clockwise
r3cc <- rotate.matrix(x = squared3, angle = 3) # upper left, need counterclockwise

r4c <- rotate.matrix(x = squared4, angle = -3) # lower left, need clockwise
r4cc <- rotate.matrix(x = squared4, angle = 3) # lower left, need counterclockwise

r1 <- plot_profilm(data = r1c, threeD = FALSE)
r2 <- plot_profilm(data = r1cc, threeD = FALSE)
r3 <- plot_profilm(data = r2c, threeD = FALSE)
r4 <- plot_profilm(data = r2cc, threeD = FALSE)
r5 <- plot_profilm(data = r3c, threeD = FALSE)
r6 <- plot_profilm(data = r3cc, threeD = FALSE)
r7 <- plot_profilm(data = r4c, threeD = FALSE)
r8 <- plot_profilm(data = r4cc, threeD = FALSE)

grid.arrange(r1,r2,r3,r4,r5,r6,r7,r8, ncol = 2)
```

# Perform manual trim 
```{r}
r1c <- r1c[10:90,10:90]
r1cc <- r1cc[10:90, 10:90]
r2c <- r2c[10:90,10:90]
r2cc <- r2cc[10:90,10:90]
r3c <- r3c[10:90,10:90]
r3cc <- r3cc[10:90,10:90]
r4c <- r4c[10:90,10:90]
r4cc <- r4cc[10:90,10:90]

r_list <- list(r1c,r1cc,r2c,r2cc,r3c,r3cc,r4c,r4cc)

r1 <- plot_profilm(data = r1c, threeD = FALSE)
r2 <- plot_profilm(data = r1cc, threeD = FALSE)
r3 <- plot_profilm(data = r2c, threeD = FALSE)
r4 <- plot_profilm(data = r2cc, threeD = FALSE)
r5 <- plot_profilm(data = r3c, threeD = FALSE)
r6 <- plot_profilm(data = r3cc, threeD = FALSE)
r7 <- plot_profilm(data = r4c, threeD = FALSE)
r8 <- plot_profilm(data = r4cc, threeD = FALSE)

grid.arrange(r1,r2,r3,r4,r5,r6,r7,r8, ncol = 2)
```

# Increase padding to prepare for rotation
```{r}

# Just increase padding by a lot (nothing specific)
scale.row = 200
scale.col = 200
  
padded_list <- lapply(r_list, FUN = function(x){
  scale(x = x, scale.row = scale.row, scale.col = scale.col)
})
  
# determine dimensions
  
dim_padded_list <- lapply(padded_list, FUN = function(x){
  dims <- dim(x)
  names(dims) <- c("rows","columns")
    return(dims)
})

p1 <- plot_profilm(data = padded_list[[1]], threeD = FALSE)
p2 <- plot_profilm(data = padded_list[[2]], threeD = FALSE)
p3 <- plot_profilm(data = padded_list[[3]], threeD = FALSE)
p4 <- plot_profilm(data = padded_list[[4]], threeD = FALSE)
p5 <- plot_profilm(data = padded_list[[5]], threeD = FALSE)
p6 <- plot_profilm(data = padded_list[[6]], threeD = FALSE)
p7 <- plot_profilm(data = padded_list[[7]], threeD = FALSE)
p8 <- plot_profilm(data = padded_list[[8]], threeD = FALSE)

grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8, ncol = 2)
```

# Try rotation algorithm
```{r}

tolerance = 0.5
t1 <- rotate(x = padded_list[[1]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "lowerRight" )
t2 <- rotate(x = padded_list[[2]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "lowerRight" )
t3 <- rotate(x = padded_list[[3]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "upperRight" )
t4 <- rotate(x = padded_list[[4]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "upperRight" )
t5 <- rotate(x = padded_list[[5]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "upperLeft" )
t6 <- rotate(x = padded_list[[6]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "upperLeft" )
t7 <- rotate(x = padded_list[[7]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "lowerLeft" )
t8 <- rotate(x = padded_list[[8]], standard_thickness = standard_thickness, tolerance = tolerance, standard_pos = "lowerLeft" )


pt1 <- plot_profilm(data = t1$matrix, threeD = FALSE)
pt2 <- plot_profilm(data = t2$matrix, threeD = FALSE)
pt3 <- plot_profilm(data = t3$matrix, threeD = FALSE)
pt4 <- plot_profilm(data = t4$matrix, threeD = FALSE)
pt5 <- plot_profilm(data = t5$matrix, threeD = FALSE)
pt6 <- plot_profilm(data = t6$matrix, threeD = FALSE)
pt7 <- plot_profilm(data = t7$matrix, threeD = FALSE)
pt8 <- plot_profilm(data = t8$matrix, threeD = FALSE)

grid.arrange(pt1,pt2,pt3,pt4,pt5,pt6,pt7,pt8, ncol = 2)
```

# So some of them did not work. Why?
# Check Trim algorithm

```{r}
tr1 <- trim(x = padded_list[[1]], standard_pos = "lowerRight")
tr2 <- trim(x = padded_list[[2]], standard_pos = "lowerRight")
tr3 <- trim(x = padded_list[[3]], standard_pos = "upperRight")
tr4 <- trim(x = padded_list[[4]], standard_pos = "upperRight")
tr5 <- trim(x = padded_list[[5]], standard_pos = "upperLeft")
tr6 <- trim(x = padded_list[[6]], standard_pos = "upperLeft")
tr7 <- trim(x = padded_list[[7]], standard_pos = "lowerLeft")
tr8 <- trim(x = padded_list[[8]], standard_pos = "lowerLeft")


ptr1 <- plot_profilm(data= tr1, threeD = FALSE)
ptr2 <- plot_profilm(data= tr2, threeD = FALSE)
ptr3 <- plot_profilm(data= tr3, threeD = FALSE)
ptr4 <- plot_profilm(data= tr4, threeD = FALSE)
ptr5 <- plot_profilm(data= tr5, threeD = FALSE)
ptr6 <- plot_profilm(data= tr6, threeD = FALSE)
ptr7 <- plot_profilm(data= tr7, threeD = FALSE)
ptr8 <- plot_profilm(data= tr8, threeD = FALSE)

grid.arrange(ptr1,ptr2,ptr3,ptr4,ptr5,ptr6,ptr7,ptr8, ncol = 2)

```

# So there is something wrong with the trimming algorithm.  Or perhaps the trace algorithm? What comes first?
# The trim algorithm does not use trace(). So fix trim()
# There was a slight typo!
# Try rotation algorithm again
# Still not working super well. I think it's because there are still zeroes at some edges after trim(). Check trace():

```{r}
trace1 <- trace(x = tr1, standard_pos = "lowerRight")
trace2 <- trace(x = tr2, standard_pos = "lowerRight")
trace3 <- trace(x = tr3, standard_pos = "upperRight")
trace4 <- trace(x = tr4, standard_pos = "upperRight")
trace5 <- trace(x = tr5, standard_pos = "upperLeft")
trace6 <- trace(x = tr6, standard_pos = "upperLeft")
trace7 <- trace(x = tr7, standard_pos = "lowerLeft")
trace8 <- trace(x = tr8, standard_pos = "lowerLeft")

print("lowerRight, need c")
trace1
print("lowerRight, need cc")
trace2
print("upperRight, need c")
trace3
print("upperRight, need cc")
trace4
print("upperLeft, need c")
trace5
print("upperLeft, need cc")
trace6
print("lowerLeft, need c")
trace7
print("lowerLeft, need cc")
trace8

```

# Trace algorithm is fine.
# Trim algorithm is fine. So what's going on? Must be the rotate one.

# Who cares about the other external standard locations. 
# Try with a bunch of different rotations

```{r}

c_ <- list()
cc_ <- list()

for(i in 1:10){
  c_[[i]] <- rotate.matrix(x = squared1, angle = -i)
  c_[[i]] <- c_[[i]][5:95,17:95] # trim off edges
}

for(i in 1:10){
  cc_[[i]] <- rotate.matrix(x = squared1, angle = i)
  cc_[[i]] <- cc_[[i]][17:95,5:95] # trim off edges
}

orig <- c(c_,cc_)

orig_plot <- lapply(orig, FUN = function(x){ x <- plot_profilm(data = x)})
do.call("grid.arrange", c(orig_plot, ncol = 10))


```


# Perform rotation
```{r}
tolerance = 0.9
threshold = 0.8

rot <- lapply(orig[1:8], FUN = function(x){
  rotate(x, standard_thickness = standard_thickness, tolerance = tolerance, threshold = threshold, standard_pos = "lowerRight") 
  })

rot_plot <- lapply(rot, FUN = function(x){ x <- plot_profilm(data = x$matrix)})

do.call("grid.arrange", c(rot_plot, ncol = 10))
```

# Plot orig vs. rotated

```{r}

degree_list <- lapply(rot, FUN = function(x){ x <- x$rot_deg})
degrees <- unlist(degree_list)

actual <- c(-1:-8,1:8)
names(actual)[1:8] <- c("need_c")
names(actual)[9:16] <- c("need_cc")

error <- actual + degrees
error
# algorithm doesn't work as well for cc rotation
```


# Plot orig vs rotated
```{r}
do.call("grid.arrange", c(orig_plot, ncol = 8))
```
```{r}
do.call("grid.arrange", c(rot_plot, ncol = 8))
```


# Need to fill edge-zeroes arising after rotation
```{r}

```